Untitled

### 2024-01-23 MSR.rmd
Update

@@

```{r}
n <- 100
e2 <- FlipCoin(n) 
cat("Banyaknya tail :", sum(e2==0), "dan Peluangnya :", sum(e2==0)/n,
    "\nBanyaknya head :", sum(e2==1), "dan Peluangnya :", sum(e2==1)/n)
```

@@

>>>>

### no 3

![](images/clipboard-1034759495.png){width="521"}

```{r}
RollDie <- function(n) sample(1:6, n, rep=T)
n <- 50
d1 <- RollDie(n)
d1
```

Selanjutnya akan menghitung berapa kali dadu sisi 3 muncul dan berapa frekuensi relatifnya.

```{r}
cat("Banyaknya tail :", sum(d1==3), "dan Frekuensi Relatifnya :", sum(d1==3)/n)
```

@@

```{r}
n <- 100
e2 <- FlipCoin(n) 
cat("Banyaknya tail :", sum(e2==0), "dan Frekuensi Relatifnya :", sum(e2==0)/n,
    "\nBanyaknya head :", sum(e2==1), "dan Frekuensi Relatifnya :", sum(e2==1)/n)
```

@@

![](images/clipboard-2216234215.png)

```{r}
Dice <- function(n){
  d <- RollDie(n)
  rolls <- numeric(0)
  for(i in 1:6) rolls = c(rolls, sum(d==i)/n)
return(rolls)
}

RollingDice <- data.frame(
  rolls.200 = Dice(200),
  rolls.1000 = Dice(1000)
) 
rownames(RollingDice) <- paste0("RF.", 1:6)
print(RollingDice)
```
